Pareto-Optimal Multistate Protein Design using Tree Graphical Models

### 2012-12-29 docs/tex/draft.tex
Additions to sim3 and changes to draft

>>>>

Current benchmarking algorithms  : 
\begin{itemize}
\item Brute Force - Simply enumerate and find the frontier
\item MCMC - Sample a number of sequences according to your energy function and keep the minimum. Should one apply Metropolis Hastings criteria usign Boltzmannm weights or something else
\item Goldstein DEE - Need a way to assign pairwise energies between amino acids. 
\item Yanover multistate DEE - Same as before but again need to assign weights. 
\end{itemize}

Also, multistate sequences designed by me are going to be good only so far as my emission and transmission weights are accurate. There needs to be a goldstandard way of assigning proper energies to the rotamers.
